\documentclass[margin,line]{res}

\usepackage{hyperref}
\usepackage{url}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


    
\begin{document}

\name{\LARGE Sean Murray} \hfill {\em \today}

\begin{resume}
\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
49 Grace Park Meadows.            & {Phone:}  (+353) 85 167 7076 \\
Drumcondra, Dublin, 9, Ireland.  & {E-mail:}  seancmry@gmail.com\\
 & {LinkedIn:}\hspace{1mm}\url{https://www.linkedin.com/in/sean-murray-577399125/} \\
 & {Website:} \url{github.com/seancmry}\\
\end{tabular}

\section{\sc Education}
{\bf Trinity College Dublin}, Dublin, Ireland. \hfill September 2014 -- present\\
%\vspace*{-.1in}
Economics (Single Honors).\\
Expected second class honors grade, graduating October 2018.

\section{\sc Professional Experience}
%%%%%%
{\bf Trinity College Dublin}, Dublin, Ireland. \hfill{May 2017 -- August 2017}\\
{\em Research Assistant}
\begin{list2} %Job Description%
\item Worked with a team under Assistant Professor Ronan Lyons to compile a dataset of US house prices for various American cities for the period between 1890-1990. 
\item Developed an application programming interface (API) using Google Maps JavaScript API as a template to display house price listings. 
\item Demonstrated the API's functions to members of the team and the Economics department of Trinity College Dublin.

\end{list2}
{\bf ImmixGroup, Inc.}, Tysons Corner, Virginia. United States. \hfill{June 2016 -- August 2016}\\
{\em Cybersecurity intern}
\begin{list2} %Job Description%
\item Processed orders and quotes for clients using Microsoft CRM.
\item Utilized SQL to alter business database fields.
\item Conducted database clean-ups, KPI report testing and call campaigns.
\item Researched NIST cybersecurity standards and delivered a presentation on my findings.
\item Developed flashcards detailing client technologies which are now used to train cold callers.
 \\
\end{list2}

{\bf Trinity Student Managed Fund}, Dublin, Ireland. \hfill{September 2015 -- December 2016}\\
{\em Analyst, Senior Analyst}
\begin{list2} %Job Description%
\item Roles in Macroeconomic, Financials, and Technology sector coverage teams.
\item Helped to manage a team of ~20 student analysts.
\item The role involved teaching new analysts the basic techniques of company analysis and valuation while guiding them through the value investing philosophy.
\item The team searched for mispriced securities, debate ideas and put together comprehensive pitches to present to the executive committee in order to secure funding.
 \\
\end{list2}
%%%%%%%%%%%

\section{\sc Additional Skills and Interests}
{\bf Programming and Technical Skills}:  JavaScript, STATA, Python, SQL, C++, C, Visual Basic, HTML, LaTeX, R, MS Office Applications, MS Visual Studio, Texmaker, MS CRM, STATA 14, MySQL, Adobe Photoshop, RStudio. \\
{\bf Operating Systems}: Windows, Linux (Ubuntu), Mac OSX.\\
{\bf Languages}: English (native); French (working proficiency); Irish (working proficiency); Russian (basic); German (basic).\\
{\bf Sports & hobbies}: travelling; hiking; reading; swimming; debating.\\
{\bf College societies}: The Hist, University Historical Society; Q Soc, Trinity LGBT Society; DU Mathsoc, Mathematics Society; The Phil, University Philosophical Society.\\

\end{resume}
\end{document}




